\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex

\subsection{Tracker}
The tracker is hosted on a remote server and tracks client connections. 
The client-side tracker interface  opens a WebSocket connection with the remote tracker, 
which registers the existence of this client. The remote tracker responds to
requests from the client for lists of peers with a given resource. When a client
publicizes that it has a resource through the tracker interface, the remote tracker updates
the list of peers with the resource to include this client, as 
long as its WebSocket connection remains open. Upon WebSocket disconnection, 
the tracker "forgets" about the client and erases all data about the client's 
held resources.

>>>>

There are two main server-side components to \zbf\. First is the tracker,
which maintains a mapping from resource hashes to the peers that have that
resource. Second is the WebRTC handshake channel, which passes information
between peers to enable them to open WebRTC data channels.

\subsection{Tracker}
The tracker is hosted on a remote server and tracks client connections.
The client-side tracker interface  opens a WebSocket connection with the remote tracker,
which registers the existence of this client. The remote tracker responds to
requests from the client for lists of peers with a given resource. When a client
publicizes that it has a resource through the tracker interface, the remote tracker updates
the list of peers with the resource to include this client, as
long as its WebSocket connection remains open. Upon WebSocket disconnection,
the tracker ``forgets'' about the client and erases all data about the client's
held resources.
